### 2021-05-19 project_ashish_monograph/results.tex
monograph updated
updated

The stability of CMS integrated luminosity for Phase I pixel detector calculated using PCC method is investigated using late Run2018D veto list.

>>>>

The stability of run 2018 CMS integrated luminosity for Phase I pixel detector calculated using PCC method is investigated by employing late Run2018D veto list.
